The Elements of Theses

### 2014-08-29 thesis/Abstract.tex
final thesis
update to thesis
some changes

The previous research for cluster-based data deduplication has concentrated on various inline solutions. The first part of the thesis work is a  highly parallel and offline solution with synchronized backup scalable for a large number of virtual machines. The key idea is to separate duplicate detection from the actual storage backup, and partition global index and detection requests among machines using fingerprint values. Then each machine conducts duplicate detection partition by partition independently with minimal memory consumption. Another optimization is to allocate and control buffer space for exchanging detection requests and duplicate summaries among machines. The memory requirement and disk usage for the proposed solution is very small while the overall throughput and backup process timing is not compromised. Our evaluation validates this and shows a satisfactory backup throughput in a large cloud setting.

@@

%\begin{germanabstract}

%\addcontentsline{toc}{chapter}{Zusammenfassung}

%\end{germanabstract}

>>>>

The previous research for cluster-based data deduplication has concentrated on various inline solutions. The first part of the thesis work is a  highly parallel and offline solution with synchronized backup scalable for a large number of virtual machines. The key idea is to separate duplicate detection from the actual storage backup, and partition global index and detection requests among machines using fingerprint values. Then each machine conducts duplicate detection partition by partition independently with minimal memory consumption. Another optimization is to allocate and control buffer space for exchanging detection requests and duplicate summaries 
among machines. The resource requirement in terms of memory and disk usage for the proposed solution is 
very small while the backup efficiency in terms of overall throughput and time is not compromised. 
Our evaluation validates this and shows a satisfactory backup throughput in a large cloud setting.

@@

### 2014-08-29 thesis/Background.tex
some changes

\chapter{Background}
\label{chap:back}
% what is the problem
Storage is the biggest challenge in virtualized cloud today.
At a cloud cluster node, each instance of a guest operating 
system runs on a virtual machine, accessing virtual hard disks 
represented as virtual disk image files in the host operating system.
Backing up virtual machines is typically done through taking snapshots,
which is a copy of the virtual machine's disk file at a given point in time.
Performing such VM snapshot backup tasks for the entire cluster is a difficult task
for several reasons: 
\begin{itemize}
\item \textbf{Huge storage demand.} Each VM contains from tens of GBs to multiple TBs of data,
the snapshots size of an entire cloud often exceeds one PB, and they need to be backed up from daily to weekly.
\item \textbf{Big network bandwidth cost.} Sending such amount of backup data requires
a lot of network bandwidth and may impede normal application activity.
\end{itemize}

As a result, data deduplication is mandatory in order to reduce the storage and bandwidth
costs of backup in cloud. But adding deduplication at cloud scale brings new
challenges against previous developed techniques:
\begin{itemize}
\item \textbf{Limited resources.} Without dedicated hardware support in backup appliances, 
VM backup and data deduplication in cloud must not race for CPU and memory resources with
existing VM activities. Compare to dedicated backup appliances which are typically equipped with
tens of GBs of memory and  multiple processors, backup service in the cloud are only allowed to use
no more than a few hundred MBs of memory, and its CPU usage must always stay low.
\item \textbf{Garbage collection for shared data.} Data management for deduplicated storage
is complicated due to the need of tracking use of every shared data block. In order to reclaim
disk space, the reference counts of
shared data blocks will need to be updated whenever a snapshot is added or deleted.
Managing reference counting for data blocks at KB level in a PB level storage is extreme difficult.
\item \textbf{Little semantic information.} For VM snapshot backup, file-level semantics are normally not provided.
Snapshot operations take place at the virtual device driver level, which
means no fine-grained file system metadata can be used to determine the changed data. 
\end{itemize}

% summary
In sum, deduplication systems designed for legacy network storage that are attached to
physical servers are too expensive and complex for virtual machines. 
Both cloud users and providers are seeking low-cost solutions to effectively backup
their data, otherwise they will be forced to backup less amount of data or less frequently,
which in return will compromise the data safty and recovery time. For example, Electronic Arts, which deploys
its data analytics platform in Amazon's AWS using several hundreds of VMs, 
avoids using Amazon's built-in snapshot storage and chooses to backup hand-picked data manuallyv for cost reasons.

To that end, this dissertation proposes low-cost deduplication storage architecture that is
collocated with other cloud services. We have learned a lot from 
% The network storage architecture designed fifteen years ago for physical
% servers 
% Backup systems have been developed to use content fingerprints to identify duplicate
% content~\cite{venti02,Rhea2008}.  
% Without an enterprise-class
% alternative, organizations are forced to use traditional solutions, which cannot
% keep up with virtual machines that are dynamic, grow rapidly in number and
% continue to demand new levels of performance and capacity.
various deduplication systems built in the past for different backup scenarios. 
In this chapter we will review the literature and discuss several system design options at high-level.
Section~\ref{back:dedup} introduces the origin and applications of data deduplication.
Section~\ref{back:optm} talks the optimization and tradeoffs in designing a deduplication storage system.
Section~\ref{back:arch} discusses design options of backup storage architecture.

\section{Deduplication}
\label{back:dedup}
Backup storage for VM snapshots in the cloud contains PBs of data from many VMs,
the data redundancy in such a data set is very high\cite{Jayaram2011, agrawal07}.
If we treat each snapshot as a single data object, the similarities between snapshots
can not be utilized. Therefore we need better method to break files into data blocks.
In the recent decad, data deduplication techniques are emerged to solve this data
redundancy problem in backup systems.
Most of data de-duplication methods can be categorized by their granularities:

@@

Content-based chunking is first proposed by Manber\cite{similar94}.
He uses Rabin's fingerprints\cite{rabin81, identify00} to sample
data in order to find similar files. This technique computes
fingerprints of all possible substrings of a certain
length in a file and chooses a subset of these fingerprints
based on their values,  e.g., if $(fingerprint(s)\ mod\ a) = b$, where
$s$ is a substring,
$a$ and $b$ are pre-defined values, then the position of substring $s$
is considered as a breakpoint. 
These breakpoints provide 
modification-resistant boundaries that seperate the file
into many small chunks. A sequence of hash values of such chunks
is a compact representation of a file, that is then used to compare
against other fingerprinted files.

There are pathological cases in finding breakpoints, for example,
a long extent of zeros may never contain a breakpoint. Thus, LBFS\cite{lbfs01}
introduces min and max thresholds to the chunk size: when scanning the file
sequentially for breakpoints, if the distance between current substring 
and previous breakpoint is less than the minimum threshold, then it is skipped;
if the distance reaches the maximum threshold, then a breakpoint
is enforced. This method also reduces the computation because less substrings
are checked. In order to increase the chance of finding a breakpoint between
two thresholds, Kave\cite{frame05}
proposes the two divisors idea, in addition to have a standard breaking condition,
a weaker breaking condition is used to find backup breakpoints.

@@

Since content-based chunking strips files into data blocks 
and identify them by content hash,
it is very natrual to build CAS system base on it.
Jumbo Store and others\cite{jumbo07,efficient_dedup05,you06} encodes directory tree snapshots
into a graph whose nodes are data blocks and edges
are hash value pointers.
Directory metadata, file metadata and data chunk are all
represented in the form of variable-size data blocks that indetified by content hash.
A object which encapsulate metadata also has a list of hash indentifiers 
that point to other blocks it contains.
Such a de-duplication storage system has some great advantages 
in terms of space efficiency, file transmission efficiency (through a LBFS-like protocol), 
and data integrity checking (by verifying the hash).

Cumulus\cite{cumulus09} is a client side backup tool to store 
file system snapshots in exist cloud storage such as S3.
To create a snapshot, Cumulus uses content-based chunking to break files into data blocks,
then compare (by hash) them to the list of stored blocks (in local logs).
New blocks will be packed and compressed into a segment file, and sent to server.
The advantage of Cumulus is portability, because it makes 
the de-duplication backup totoally opaque to the server.
However, without the de-duplication support from protocol and server side, 
it's hard to have efficent storage management, and from server's perspective,
snapshots from many users still contain much redundant data.

\section{Optimizations and Tradeoffs}
\label{back:optm}
Many previous studies on data deduplication focus on the disk bottleneck problem,
which refers to the key performance challenge in finding duplicate blocks. 
Let's consider a single machine in cluster which hosts many VMs and has 10 TB of virtual disks in total,
if it needs to be backed up daily, then the performance target would be 115 MB/sec on each machine.
Given a block size of 4 KB, a deduplication system must process approximately 28,900 blocks per second.
An in-memory index of all block fingerprints could easily achieve this performance, but the size of the index would limit system size and increase system cost. 
If we use 20 bytes as block fingerprint size, then supporting 10 TB worth of unique blocks, would require 50 GB just to store the fingerprints.
An alternative approach is to maintain an on-disk index of block fingerprints and use a cache to accelerate block index accesses. Unfortunately, a traditional cache would not be effective for this workload. Since fingerprint values are random, there is no spatial locality in the block index accesses. 
With low cache hit ratios, most index lookups require disk operations. If each index lookup requires a disk access which may take 10 msec and 8 disks are used for index lookups in parallel, the write throughput will be about 6.4MB/sec, which is far from the throughput goal of deduplicating at 115 MB/sec for our cloud backup scenario, and don't forget that this goal
is conservative since VM users generally want the backup task to finish in tens of minutes without affecting their normal
application activities.

@@

Most of approaches discussed above focus on optimization of inline deduplication
performance by sacraficing a small percent of deduplication efficiency.
In our cloud backup scenario, we must always satisfy the low resource usage constraints while 
providing sustainable good throughput. As a result, we consider to sacrifice other performance metrics 
to achieve our design goals, which we descibe as below:
% In addition, none of them have considered the impact
% of deduplication on fault tolerance in the cluster-based environment that we have considered
% in this dissertation.

% \section{Tradeoff in Design Goals}
% \label{back:trade}
Given we are designing scalable low-cost collocated deduplication solutions,
the effectiveness of a deduplication system is determined 
by the extent to which it can achieve three mutually competing goals: 
deduplication efficiency, throughput, and job turnaround time. 
Deduplication efficiency refers to
how well the system can detect and share duplicate data
units which is its primary compression goal. Throughput refers
to the rate at which data can be transferred in and out of
the system, and constitutes the main performance metric.
Job turnaround time is the total time for a backup job from submit to finish.
All three metrics are important. Good dedupe efficiency 
reduces the storage cost. High throughput
is particularly important because it can enable fast backups, 
minimizing the length of a backup window. 
Job turnaround time reflects how fast primary storage 
can be released from backup related I/O activity.
Among the three goals, it is easy to optimize any two of them,
but not all. To get good deduplication efficiency, 
it is necessary to perform data indexing for duplicate detection.
The indexing metadata size grows linearly with the capacity of the system. 
Keeping this metadata in memory,
would yield good throughput. 
But the amount of available RAM would set a hard limit to the scalability of the
system. Partition indexing metadata man remove
the scalability limit, but significantly hurt job turnaround time.
Finally, we can optimize for both throughput and turnaround time, 
, but then we lose deduplication as there's no cheap solution to search all metadata quickly. 
Achieving all three goals is a non-trivial task.

@@

This dissertation studies two low-cost deduplication design options with different tradeoffs. 
Chapter~\ref{chap:offline} gives a synchronous parallel deduplication design that
sacrifices the job turnaround time to achieve high throughput and deduplication efficiency.
Chapter~\ref{chap:inline} describes an multi-level selective deduplication solution
that comprises deduplication efficiency to improve throughput and job turnaround time.

>>>>

\chapter{Background}
\label{chap:back}
% what is the problem

%Storage is the biggest challenge in virtualized cloud today.
At a cloud cluster node, each instance of a guest operating 
system runs on a virtual machine, accessing virtual hard disks 
represented as virtual disk image files in the host operating system.
Virtual machine backup is typically conducted through a snapshot,
which is a copy of the virtual machine's disk files at a given time.
Performing VM snapshot backup for the entire cluster is difficult 
for several reasons: 
\begin{itemize}
\item \textbf{Huge storage demand.} The size of each VM snapshot varies from tens of gigabytes to multiple 
terabytes while the total snapshot size of an entire cloud cluster is often  in a petabyte level.
Such data needs to be backed up daily or weekly.
\item \textbf{Big network bandwidth cost.} Sending such a large amount of snapshot data requires
a large network bandwidth and may impede normal application activities.
\end{itemize}

As a result, data deduplication is necessary in order to reduce the storage and bandwidth
costs of backup in a cloud cluster. But adding deduplication at a cloud scale brings new
challenges against previous developed techniques:
\begin{itemize}
\item \textbf{Limited resources.} Without dedicated hardware support in backup appliances, 
VM backup and data deduplication in cloud must not race for CPU and memory resources with
existing VM activities. Compare to dedicated backup appliances which are typically equipped with
tens of GBs of memory and  multiple processors, backup service in the cloud are only allowed to use
no more than a few hundred MBs of memory, and its CPU usage must always stay low.
\item \textbf{Garbage collection for shared data.} Data management for deduplicated storage
is complicated due to the need of tracking use of every shared data block. In order to reclaim
disk space, the reference counts of
shared data blocks will need to be updated whenever a snapshot is added or deleted.
Managing reference counting for data blocks at KB level in a PB level storage is extreme difficult.
\item \textbf{Little semantic information.} For VM snapshot backup, file-level semantics are normally not provided.
Snapshot operations take place at the virtual device driver level, which
means no fine-grained file system metadata can be used to determine the changed data. 
\end{itemize}

% summary
In summary, deduplication systems designed for legacy network storage that are attached to
physical servers are too expensive and complex for virtual machines. 
Both cloud users and providers are seeking low-cost solutions to effectively backup
their data, otherwise they will be forced to backup less amount of data or less frequently,
which in return will compromise the data safety and recovery time. For example, Electronic Arts, which deploys
its data analytics platform in Amazon's AWS using several hundreds of VMs, 
avoids using Amazon's built-in snapshot storage and chooses to backup hand-picked data manually for cost reasons.

To that end, this dissertation proposes low-cost deduplication storage architecture that is
collocated with other cloud services. We have learned a lot from 
% The network storage architecture designed fifteen years ago for physical
% servers 
% Backup systems have been developed to use content fingerprints to identify duplicate
% content~\cite{venti02,Rhea2008}.  
% Without an enterprise-class
% alternative, organizations are forced to use traditional solutions, which cannot
% keep up with virtual machines that are dynamic, grow rapidly in number and
% continue to demand new levels of performance and capacity.
various deduplication systems built in the past for different backup scenarios. 
In this chapter we will review the literature and discuss several system design options at high-level.
Section~\ref{back:dedup} introduces the origin and applications of data deduplication.
Section~\ref{back:optm} talks the optimization and tradeoff in designing a deduplication storage system.
Section~\ref{back:arch} discusses design options of backup storage architecture.

\section{Deduplication}
\label{back:dedup}
Backup storage for VM snapshots in the cloud contains PBs of data from many VMs,
the data redundancy in such a data set is very high\cite{Jayaram2011, agrawal07}.
If we treat each snapshot as a single data object, the similarities between snapshots
can not be utilized. Therefore we need better method to break files into data blocks.
In the recent decade, data deduplication techniques are emerged to solve this data
redundancy problem in backup systems.
Most of data de-duplication methods can be categorized by their granularities:

@@

Content-based chunking is first proposed by Manber\cite{similar94}.
He uses Rabin's fingerprints\cite{rabin81, identify00} to sample
data in order to find similar files. This technique computes
fingerprints of all possible substrings of a certain
length in a file and chooses a subset of these fingerprints
based on their values,  e.g., if $(fingerprint(s)\ mod\ a) = b$, where
$s$ is a substring,
$a$ and $b$ are pre-defined values, then the position of substring $s$
is considered as a breakpoint. 
These breakpoints provide 
modification-resistant boundaries that separate the file
into many small chunks. A sequence of hash values of such chunks
is a compact representation of a file, that is then used to compare
against other fingerprinted files.

There are pathological cases in finding breakpoints, for example,
a long extent of zeros may never contain a break point. Thus, LBFS\cite{lbfs01}
introduces min and max thresholds to the chunk size: when scanning the file
sequentially for breakpoints, if the distance between current substring 
and previous breakpoint is less than the minimum threshold, then it is skipped;
if the distance reaches the maximum threshold, then a breakpoint
is enforced. This method also reduces the computation because less substrings
are checked. In order to increase the chance of finding a breakpoint between
two thresholds, Kave\cite{frame05}
proposes the two divisors idea, in addition to have a standard breaking condition,
a weaker breaking condition is used to find backup breakpoints.

@@

Since content-based chunking strips files into data blocks 
and identify them by content hash,
it is very natural to build CAS system base on it.
Jumbo Store and others\cite{jumbo07,efficient_dedup05,you06} encodes directory tree snapshots
into a graph whose nodes are data blocks and edges
are hash value pointers.
Directory metadata, file metadata and data chunk are all
represented in the form of variable-size data blocks that identified by content hash.
A object which encapsulate metadata also has a list of hash identifiers 
that point to other blocks it contains.
Such a de-duplication storage system has some great advantages 
in terms of space efficiency, file transmission efficiency (through a LBFS-like protocol), 
and data integrity checking (by verifying the hash).

Cumulus\cite{cumulus09} is a client side backup tool to store 
file system snapshots in exist cloud storage such as S3.
To create a snapshot, Cumulus uses content-based chunking to break files into data blocks,
then compare (by hash) them to the list of stored blocks (in local logs).
New blocks will be packed and compressed into a segment file, and sent to server.
The advantage of Cumulus is portability, because it makes 
the de-duplication backup totally opaque to the server.
However, without the de-duplication support from protocol and server side, 
it's hard to have efficient storage management, and from server's perspective,
snapshots from many users still contain much redundant data.

\section{Optimization and Tradeoff}
\label{back:optm}
Many previous studies on data deduplication focus on the disk bottleneck problem,
which refers to the key performance challenge in finding duplicate blocks. 
Let's consider a single machine in cluster which hosts many VMs and has 10 TB of virtual disks in total,
if it needs to be backed up daily, then the performance target would be 115 MB/sec on each machine.
Given a block size of 4 KB, a deduplication system must process approximately 28,900 blocks per second.
An in-memory index of all block fingerprints could easily achieve this performance, but the size of the index would limit system size and increase system cost. 
If we use 20 bytes as block fingerprint size, then supporting 10 TB worth of unique blocks, would require 50 GB just to store the fingerprints.
An alternative approach is to maintain an on-disk index of block fingerprints and use a cache to accelerate block index accesses. Unfortunately, a traditional cache would not be effective for this workload. Since fingerprint values are random, there is no spatial locality in the block index accesses. 
With low cache hit ratios, most index lookups require disk operations. If each index lookup requires a disk access which may take 10 msec and 8 disks are used for index lookups in parallel, the write throughput will be about 6.4MB/sec, which is far from the throughput goal of deduplicating at 115 MB/sec for our cloud backup scenario, and don't forget that this goal
is conservative since VM users generally want the backup task to finish in tens of minutes without affecting their normal
application activities.

@@

Most of approaches discussed above focus on optimization of inline deduplication
performance by sacrificing a small percent of deduplication efficiency.
In our cloud backup scenario, we must always satisfy the low resource usage constraints while 
providing sustainable good throughput. As a result, we consider to sacrifice other performance metrics 
to achieve our design goals, which we describe as below:
% In addition, none of them have considered the impact
% of deduplication on fault tolerance in the cluster-based environment that we have considered
% in this dissertation.

% \section{Tradeoff in Design Goals}
% \label{back:trade}
Given we are designing scalable low-cost collocated deduplication solutions,
the effectiveness of a deduplication system is determined 
by the extent to which it can achieve three mutually competing goals: 
deduplication efficiency, throughput, and job turnaround time. 
Deduplication efficiency refers to
how well the system can detect and share duplicate data
units which is its primary compression goal. Throughput refers
to the rate at which data can be transferred in and out of
the system, and constitutes the main performance metric.
Job turnaround time is the total time for a backup job from submit to finish.
All three metrics are important. Good deduplication efficiency 
reduces the storage cost. High throughput
is particularly important because it can enable fast backups, 
minimizing the length of a backup window. 
Job turnaround time reflects how fast primary storage 
can be released from backup related I/O activity.
Among the three goals, it is easy to optimize any two of them,
but not all. To get good deduplication efficiency, 
it is necessary to perform data indexing for duplicate detection.
The indexing metadata size grows linearly with the capacity of the system. 
Keeping this metadata in memory,
would yield good throughput. 
But the amount of available RAM would set a hard limit to the scalability of the
system. Partition indexing metadata man remove
the scalability limit, but significantly hurt job turnaround time.
Finally, we can optimize for both throughput and turnaround time, 
, but then we lose deduplication as there's no cheap solution to search all metadata quickly. 
Achieving all three goals is a non-trivial task.

@@

This dissertation studies two low-cost deduplication design options with different tradeoff. 
Chapter~\ref{chap:offline} gives a synchronous parallel deduplication design that
sacrifices the job turnaround time to achieve high throughput and deduplication efficiency.
Chapter~\ref{chap:inline} describes an multi-level selective deduplication solution
that comprises deduplication efficiency to improve throughput and job turnaround time.

### 2014-08-29 thesis/Introduction.tex
update to thesis
some changes

\chapter{Introduction}
\label{chap:intro}
\section{Problem Statement and Motivation}
\label{intro:prob}
The ubiquity of the cloud computing has resulted in the 
widespread availability of cloud based services and applications accessible through 
the network. Examples include online storage services, big data analysis, and various websites.
In such a cluster-based cloud environment,
each physical machine runs a number of virtual machines as  instances of a guest operating system 
to contain different kind of user applications,
and their data are stored in virtual hard disks which are represented 
as virtual disk image files in the host operating system.
Frequent snapshot backup of virtual disk images is critical to increase  the service reliability
and protect data safty.
For example, the Aliyun cloud, which is  the largest cloud service provider by Alibaba in China, 
automatically conducts  the backup of virtual disk images to all active users every day.

The cost of supporting a large number of concurrent backup streams is high
because of the huge storage demand. 
If such VM snapshot data are plainly backed up without any duplicate reduction, storage waste would be 
extreme high. For example, a fresh Windows server 2008 installation costs 25 GB on the virtual disk,
and they are almost certianly duplicated with other Windows VM instances\cite{common07, pedal96}.
Using a separate  backup service with full deduplication support~\cite{venti02,bottleneck08}
can effectively identify and remove content duplicates among snapshots, 
but such a solution can be expensive. There is also a large amount of 
network traffic to transfer  data from the host machines to the backup facility
before duplicates are removed.

Unlike the previous work dealing with general file-level
backup and deduplication inside a centralized storage appliance, our problem is focused on virtual
disk image backup in a cluster of machines. Although we treat each virtual disk as a
file logically, its size is very large. On the other hand, we need
to support parallel backup of a large number of virtual disks
in a cloud every day. One key requirement we face at busy clouds
 is that VM snapshot backup should only use a minimal
amount of system resources so that most of resources is kept
for regular cloud system services or applications. Thus our
objective is to exploit the characteristics of VM snapshot data
and pursue a cost-effective deduplication solution. Another
goal is to decentralize VM snapshot backup and localize
deduplication as much as possible, which brings the benefits
for increased parallelism and fault isolation.

Despite its importance, storage deduplication remains a challenging task for cloud storage providers. 
And this is especially true for resource constrained large scale public VM cloud. 
In recognizing this importance and
the associated challenges,  my thesis is that

\textit{It  is  possible  to  build  an efficient, scalable, and fault tolerant backup storage
supporting highly accurate deduplication with sustainable high throughput
and easy management on deduplicated data.}

In  other  words,  the  main  goal  of this  study  is  to  answer  the  following 
question.  Given a large scale VM cluster running tens of thousand of VMs, 
how can such a snapshot backup service identify whether a piece of data in VM disk
really needs to backup? And how to manage backup data under complex sharing relationship?
This dissertation investigates 
techniques  in  building  a snapshot storage architecture that provides 
low-cost deduplication support for large VM clouds.  In particular,  it 
contains the following contributions to establish my thesis:

\begin{itemize}
\item A design of low-cost multi-stage parallel deduplication solution for automically batched deduplication.
\item An inline multi-level deduplication scheme with similarity guided local detection and popularity guided global detection.
\item The development and analysis of a VM-centric storage approach which considers fault isolation and integrates multiple duplicate detection strategies.
\item Fast and efficient garbage collection with approximate snapshot deletion and leak repair.
\end{itemize}

In general, this  dissertation  study  is  built  upon  a  large  body  of previous  research 
in storage deduplication and distributed storage systems.  The goal 
of this work is to provide low-cost deduplication support and storage management for 
large scale resource-constrained VM cloud. This solution should be collocated with existing
cloud infrastructure services and require no dedicated hardware support. It also needs to
accomplish good deduplication efficiency and does comprise the data reliability due to the
inherent volatility of commodity hardware.
Under the  above consideration, our system is designed to support multiple levels of deduplication
depending on backup requirements. The objective is to provide satisfactory deduplication efficiency
and high throughput with the emphasis on low resource usage and fault tolerancy.

\section{Dissertation Organization}
\label{intro:organ}
The rest of this dissertation is organized as follows.  
Chapter~\ref{chap:back} gives an introduction to the history and background of thesis problems.
Chapter~\ref{chap:overview} presents the overall VM snapshot storage architecture.
Chapter~\ref{chap:offline}  describes a synchronous and parallel deduplication scheme for offline batched complete deduplication.
Chapter~\ref{chap:inline} studies a multi-level selective deduplication solution for inline deduplication.
Chapter~\ref{chap:data}  describes a VM-centric storage management with approximate deletion.
Chapter~\ref{chap:concl}  concludes this  dissertation  and  briefly discusses some potential future work.

>>>>

\chapter{Introduction}
\label{chap:intro}
\section{Problem Statement and Motivation}
\label{intro:prob}
The ubiquity of the cloud computing has resulted in the 
widespread availability of cluster-based services and applications accessible through 
the Internet. Examples include online storage services, big data analytics, and e-commerce websites.
In such a cluster-based cloud environment,
each physical machine runs a number of virtual machines as  instances of a guest operating system 
to contain different kind of user applications,
and their data is stored in virtual hard disks which are represented 
as virtual disk image files in the host operating system.
Frequent snapshot backup of virtual disk images is critical to increase  the service reliability
and protect data safty.
For example, the Aliyun cloud, which is  the largest cloud service provider by Alibaba in China, 
automatically conducts  the backup of virtual disk images to all active users every day.

The cost of supporting a large number of concurrent backup streams is high
because of the huge storage demand. 
If such VM snapshot data is plainly backed up without any duplicate reduction, storage waste would be 
extreme high. For example, a fresh Windows server 2008 installation costs 25 GB on the virtual disk,
and they are almost certianly duplicated with other Windows VM instances\cite{common07, pedal96}.
Using a separate  backup service with full deduplication support~\cite{venti02,bottleneck08}
can effectively identify and remove content duplicates among snapshots, 
but such a solution can be expensive. There is also a large amount of 
network traffic to transfer  data from the host machines to the backup facility
before duplicates are removed.

Unlike the previous work dealing with general file-level
backup and deduplication inside a centralized storage appliance, our research is focused on virtual
disk image backup in a cluster of machines. Although we treat each virtual disk as a
file logically, its size is very large. On the other hand, we need
to support parallel backup of a large number of virtual disks
in a cloud every day. One key requirement we face at a busy cloud cluster
 is that VM snapshot backup should only use a minimal
amount of system resources so that most of resources is kept
for regular cloud system services or applications. Thus our
objective is to exploit the characteristics of VM snapshot data
and pursue a cost-effective deduplication solution. Another
goal is to decentralize VM snapshot backup and localize
deduplication as much as possible, which brings the benefits
for increased parallelism and fault isolation.

Despite its importance, storage deduplication remains a challenging task for cloud storage providers,
especially for resource-constrained large-scale public VM clouds. 
In recognizing this importance and
the associated challenges,  my thesis is that

\textit{It  is  possible  to  build  an efficient, scalable, and fault-tolerant backup service
supporting highly accurate deduplication with sustainable high throughput.}

In  other  words,  the  main  goal  of this  study  is  to  answer  the  following 
question.  Given a large scale VM cluster running tens of thousand of VMs, 
how can such a snapshot backup service identify whether a piece of data in VM disk
really needs a backup? And how to manage backup data under complex sharing relationship?
This dissertation investigates 
techniques  in  building  a snapshot storage architecture that provides 
low-cost deduplication support for large VM clouds.  In particular,  it 
contains the following contributions to establish my thesis:

\begin{itemize}
\item The design of a low-cost multi-stage parallel deduplication solution for automically batched deduplication.
\item An inline multi-level deduplication scheme with similarity-guided local detection and 
popularity-guided global detection.
\item The development and analysis of a VM-centric storage approach which considers fault isolation and integrates multiple duplicate detection strategies.
\item Fast and efficient garbage collection with approximate snapshot deletion and leak repair.
\end{itemize}

In general, this  dissertation  study  is  built  upon  a  large  body  of previous  research 
in storage deduplication and distributed storage systems.  The goal 
of this work is to provide low-cost deduplication support and storage management for 
large-scale resource-constrained VM clouds. This solution should be collocated with existing
cloud infrastructure services and require no dedicated hardware support. It also needs to
accomplish good deduplication efficiency and does not comprise the data reliability due to the
inherent volatility of commodity hardware.
Under the  above consideration, our system is designed to support multiple levels of deduplication
depending on backup requirements. The objective is to provide satisfactory deduplication efficiency
and high throughput with the emphasis on low resource usage and fault tolerance.

\section{Dissertation Organization}
\label{intro:organ}
The rest of this dissertation is organized as follows.  
Chapter~\ref{chap:back} gives the background of thesis problems.
Chapter~\ref{chap:overview} presents the overall VM snapshot storage architecture.
Chapter~\ref{chap:offline}  describes a synchronous and parallel deduplication scheme for batched complete deduplication.
Chapter~\ref{chap:inline} studies a multi-level selective deduplication solution for inline deduplication.
Chapter~\ref{chap:data}  describes a VM-centric storage management with approximate deletion.
Chapter~\ref{chap:concl}  concludes this  dissertation  and  briefly discusses some potential future work.
